Analysis for Biracial Grade Retention Project

### 2022-09-02 analysis/analysis.Rmd
Add subheaders for resource differentials section

# Differences in Cultural and Family Resources

@@

@@

>>>>

# Differences in Family Resources

## Full tables of SES and cultural resources

@@

## Counterfactual models by resource differentials

@@

### Senstivity tests separating SES and cultural differences

Lets do the same procedure but I want to isolate the role of SES vs cultural (foreign-born and language).

For ease of use, I am just going to plug in values here for the other resources rather than dummy everything up.

```{r cf-ses-isolate, warning=FALSE, fig.cap="Counterfactual probability of being behind grade for biracial respondents in comparison to their monoracial comparison groups if the only differences between groups were SES resources (household income, parental education, home ownership, and whether parents are married). 83.4% confidence bands shown around each estimate. Non-overlap in confidence bands roughly indicates statistically significant difference at the 5% level."}
cf_df_ses <- cf_df
cf_df_ses$foreign_born <- FALSE
cf_df_ses$foreign_born_father <- FALSE
cf_df_ses$foreign_born_mother <- FALSE
cf_df_ses$spk_eng <- "Yes"
cf_df_ses$spk_eng_father <- "Yes"
cf_df_ses$spk_eng_mother <- "Yes"

coefs_cf_ses <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df_ses, race==x)
  means_margin <- marg(model_full, "year", data=temp)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows()

coef_table_cf_ses <- create_coef_table(coefs_cf_ses)

ggplot(coef_table_cf_ses, aes(x=term, y=estimate, color=multiracial,
                          ymin=estimate-1.386*se, ymax=estimate+1.386*se))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=estimate_mid-1.386*se_mid,
                ymax=estimate_mid+1.386*se_mid, fill=multiracial), 
            color=NA, alpha=0.2)+
  geom_linerange(data=subset(coef_table_cf_ses, multiracial))+
  geom_point()+
  coord_flip()+
  facet_wrap(~mrace, scales="free_y")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())+
  scale_color_manual(values=c("grey40","red"))+
  scale_fill_manual(values=c("grey40","red"))+
  scale_linetype_manual(values=c(3,1))+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="average adjusted predicted probability of being behind expected grade")
```

```{r cf-culture-isolate, warning=FALSE, fig.cap="Counterfactual probability of being behind grade for biracial respondents in comparison to their monoracial comparison groups if the only differences between groups were cultural resources (foreign-born status and English proficiency). 83.4% confidence bands shown around each estimate. Non-overlap in confidence bands roughly indicates statistically significant difference at the 5% level."}
cf_df_culture <- cf_df
cf_df_culture$family_income <- mean(cf_df_culture$family_income)
cf_df_culture$own_home <- TRUE
cf_df_culture$degree_father <- "BA"
cf_df_culture$degree_mother <- "BA"
cf_df_culture$parents_married <- TRUE

coefs_cf_culture <- lapply(unique(acs$race), function(x) {
  temp <- subset(cf_df_culture, race==x)
  means_margin <- marg(model_full, "year", data=temp)[[1]]
  return(tibble(term=x, estimate=means_margin$Margin, 
                se=means_margin$Standard.Error))
}) %>%
  bind_rows()

coef_table_cf_culture <- create_coef_table(coefs_cf_culture)

ggplot(coef_table_cf_culture, aes(x=term, y=estimate, color=multiracial,
                          ymin=estimate-1.386*se, ymax=estimate+1.386*se))+
  geom_rect(aes(xmax=Inf, xmin=-Inf, ymin=estimate_mid-1.386*se_mid,
                ymax=estimate_mid+1.386*se_mid, fill=multiracial), 
            color=NA, alpha=0.2)+
  geom_linerange(data=subset(coef_table_cf_culture, multiracial))+
  geom_point()+
  coord_flip()+
  facet_wrap(~mrace, scales="free_y")+
  theme_bw()+
  theme(legend.position = "none", panel.grid = element_blank())+
  scale_color_manual(values=c("grey40","red"))+
  scale_fill_manual(values=c("grey40","red"))+
  scale_linetype_manual(values=c(3,1))+
  scale_y_continuous(labels = scales::percent)+
  labs(x=NULL,
       y="average adjusted predicted probability of being behind expected grade")
```

The results are a lot messier for cultural differences, partly because of the opposite effect of foreign-born parents. In most cases, differences point to an in-between status when there is any daylight between the constituent groups. So, its the SES effects that are really pulling this toward the lower group.

## Summary table of resource differences
